|

### 2016-05-31 Benchmark/MSGF-Benchmark/msgf-benchmark2.Rmd
benchmark

pnnl <- mzid_pnnl[, c("Scan", "MSGFDB_SpecEValue", "Peptide")]
pnnl <- pnnl[!duplicated(pnnl$Scan),]
pnnl$Peptide <- substr(as.character(pnnl$Peptide),1,nchar(as.character(pnnl$Peptide))-2)
pnnl$Peptide <- substr(as.character(pnnl$Peptide),3,nchar(as.character(pnnl$Peptide)))
docker       <- frm_docker[,c("Scan","Spec_Evalue","PepSeq")]
```

@@

#3. Differences. Spec eValue = `r evalue` 
### a. From PNNL
```{r, echo=F}
c_pnnl = pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
print(paste("Remaining peptides:",nrow(c_pnnl)))
# print("====== head ======")
# head(c_pnnl,2)
# print("====== tail ======")
# tail(c_pnnl,2)

@@

#4. Differences. Spec eValue = `r evalue` 
### a. From PNNL
```{r, echo=F}
c_pnnl = pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
print(paste("Remaining peptides:",nrow(c_pnnl)))
# print("====== head ======")
# head(c_pnnl,2)
# print("====== tail ======")
# tail(c_pnnl,2)

@@

#5. Differences. Spec eValue = `r evalue` 
### a. From PNNL
```{r, echo=F}
c_pnnl = pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
print(paste("Remaining peptides:",nrow(c_pnnl)))
# print("====== head ======")
# head(c_pnnl,2)
# print("====== tail ======")
# tail(c_pnnl,2)

@@

>>>>

pnnl <- mzid_pnnl[, c("Scan", "MSGFDB_SpecEValue", "Peptide")]
#pnnl <- pnnl[!duplicated(pnnl$Scan),]
pnnl$Peptide <- substr(as.character(pnnl$Peptide),1,nchar(as.character(pnnl$Peptide))-2)
pnnl$Peptide <- substr(as.character(pnnl$Peptide),3,nchar(as.character(pnnl$Peptide)))
docker       <- frm_docker[,c("Scan","Spec_Evalue","PepSeq")]
```

@@

#3. Differences. Spec eValue Threshold= `r evalue` 
### a. From PNNL
```{r, echo=F}
c_pnnl = pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
print(paste("Remaining peptides:",nrow(c_pnnl)))
# print("====== head ======")
# head(c_pnnl,2)
# print("====== tail ======")
# tail(c_pnnl,2)

@@

#4. Differences. Spec eValue Threshold = `r evalue` 
### a. From PNNL
```{r, echo=F}
c_pnnl = pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
print(paste("Remaining peptides:",nrow(c_pnnl)))
# print("====== head ======")
# head(c_pnnl,2)
# print("====== tail ======")
# tail(c_pnnl,2)

@@

#5. Differences. Spec eValue Threshold = `r evalue` 
### a. From PNNL
```{r, echo=F}
c_pnnl = pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
print(paste("Remaining peptides:",nrow(c_pnnl)))
# print("====== head ======")
# head(c_pnnl,2)
# print("====== tail ======")
# tail(c_pnnl,2)

@@

#6. Differences between results from PNNL and DTA file from PNNL.

MSGF+ was run against `TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_dta.txt` using the same command (10 ppm, without Docker). 
```{r echo=F, cache=T, warning=F}
setwd("~/Dropbox/_SPACE/Benchmark/11")
dta_mzid  <- mzID(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_msgfplus.mzid")
#dta_mzml  <- readMSData(files = file_mzml[2])
#dta       <- read.table("TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_msgfdb.tsv", sep="\t", header = T)
dta       <- flatten(dta_mzid)
colnames(dta)[2] <- "Scan"

```
```{r echo=F}
dta_merge <- merge(x=dta[,c("Scan","ms-gf:specevalue","pepseq")], y=pnnl, by="Scan", all=T)

same      <- dta_merge[(dta_merge$MSGFDB_SpecEValue==dta_merge$'ms-gf:specevalue') & (dta_merge$Peptide==dta_merge$pepseq),]

same      <- same[!is.na(same$Scan),]
print(paste("Exact match:", nrow(same)))
print(paste("From PNNL:", names(same)[2],names(same)[3],". From Docker:", names(same)[4],names(same)[5]))
print(head(same,2))
diff_spec      <- dta_merge[(dta_merge$MSGFDB_SpecEValue!=dta_merge$'ms-gf:specevalue') & (dta_merge$Peptide==dta_merge$pepseq),]

diff_spec <- diff_spec[!is.na(diff_spec$Scan),]
print(paste("Different Spec eValue:", nrow(diff_spec)))
tail(diff_spec,3)
diff_pep      <- dta_merge[(dta_merge$MSGFDB_SpecEValue!=dta_merge$'ms-gf:specevalue') & (dta_merge$Peptide!=dta_merge$pepseq),]

diff_pep  <- diff_pep[!is.na(diff_pep$Scan),]
print(paste("Different ID and Spec eValue:", nrow(diff_pep)))
tail(diff_pep,3)
```
